Swarm coordination through perimeter detection

### 2017-03-20 paper.tex
First Draft

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Swarm coordination through perimeter detcetion}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
This chapter identifies the effect a \textit{destination vector} has upon the motion of a swarm. Three coordination techniques are applied to a swarm and metrics are used to identify the effects. The three coordination techniques are: full perimeter detection, where only edge based agents will have a \textit{destination vector} applied. Partial perimeter detection, where a subset of the perimeter agents are detected and finally all agents in the swarm having a \textit{destination vector} applied. For all the experiments the base parameters of the swarm are fixed ensuring that the only variable will be the \textit{destination vector} that is applied by the coordinating agents. This process allows the impact of the algorithms to be isolated and compared. Section~\ref{sec:AlternateBias1}~discusses the potential variations to the base parameters and the effects this has on controlling the impact of the weightings.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SampleSwarm200-1}
\end{center}
\caption[Sample swarm 200 agents initial state]{Sample swarm 200 agents initial state (\textit{screen shot from simulator})\label{fig:SampleSwarm200-1}}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{| p{2.5cm} | c | p{7cm} |}
\hline
\bf Weight \bf Component & \bf Hexagonal & \bf Description \\ \hline
Sample Rate & 100 & ms - Unit sampling interval\\  \hline
$k_c$ & 5 & weight adjuster for cohesion vector\\  \hline
$k_r$ & 15 & weight adjuster for repulsion  vector\\  \hline
$k_d$ & 0/100 & weight adjuster for destination vector 0 for static baseline 100 for destination based\\  \hline
Neighbour Distance & 70 & units\\  \hline
Agent Boundary & 80 & units\\  \hline
Speed & 20 & units/s\\  \hline
\end{tabular}\caption{Swarm Weighted Model} \label{tab:DynamicPhysics1}
\end{center}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineMagnitude1}
\end{center}
\caption{Baseline internal movement - magnitude\label{coord:BaselineMagnitude1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineDistance1}
\end{center}
\caption{Baseline internal movement - distance\label{coord:BaselineDistance1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmPathBaseline}
\end{center}
\caption{Baseline swarm path\label{coord:SwarmPathBaseline1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=7cm]{figures/Monolithic2}
\end{center}
\caption[Monolithic agents]{Monolithic agents (Circles indicate all agents are using GPS, \textit{screen shot from simulator}) \label{reduced:Monolithic1}}
\end{figure}

\subsection{Baseline and effect of no perimeter detection\label{section:compareBaselineNoPerimeter}}
To identify the effect of the all-agents algorithm the simulation is executed using the same parameters as the baseline swarm with the added \textit{destination vector} on all the agents. The effect of introducing this bias on the swarms internal characteristics is shown in~Figures~\ref{reduced:BaselineAllAgentsMag1} and~\ref{reduced:BaselineAllAgentsDist1}.
%BASELINE-ALLAGENTS-MAG.py
\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllAgentsMag1}
\end{center}
\caption{Baseline/All agents comparison \textit{inter-agent vector} magnitude\label{reduced:BaselineAllAgentsMag1}}
\end{figure}

Figure~\ref{reduced:BaselineAllAgentsMag1} shows the effect on the \textit{inter-agent vector} magnitude of the swarm: the average resultant magnitude is lower than the baseline. This is due to there being a greater distribution of \textit{inter-agent vector} magnitudes from the disturbance caused by the \textit{destination vector} on all of the agents and the swarm is therefore less cohesive. The graph also shows that there is a higher variation from the mean; again this is due to the change in the bias of all the agents. The agents are moving towards a goal and are therefore not moving to an equilibrium distribution. Figure~\ref{reduced:BaselineAllAgentsMag1}~also shows that the \textit{direction vector} increases the time it takes for the swarm to distribute the agents and although the deviation diminishes the swarm cannot overcome the \textit{direction vector's} effect and the swarm appears chaotic.
%BASELINE-ALLAGENTS-DIST.py
\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllAgentsDist1}
\end{center}
\caption{Baseline/All agents comparison (distance)\label{reduced:BaselineAllAgentsDist1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{figures/ConicalPath}
\end{center}
\caption{Conical destination trajectories\label{reduced:ConicalPath}}
\end{figure}

This effect can be seen in both the magnitudes shown in~Figure~\ref{reduced:BaselineAllAgentsMag2} and in the distances shown in~Figure~\ref{reduced:BaselineAllAgentsDist2} which both show the averages initially decreasing but then increasing again as the swarm approaches the destination. This is accompanied by a greater standard deviation caused by the \textit{direction vector} affecting the priority of the swarm as agents are drawn to the destination reducing the effect of the \textit{inter-agent vectors} creating stable structures.
%BASELINE-ALLAGENTS-MAG.py
\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllAgentsMag2}
\end{center}
\caption[Baseline/All agents magnitude comparison]{Baseline/All agents \textit{inter-agent vector} magnitude comparison (60 seconds)\label{reduced:BaselineAllAgentsMag2}}
\end{figure}
%BASELINE-ALLAGENTS-DIST.py
\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllAgentsDist2}
\end{center}
\caption{Baseline/All agents distance comparison (60 seconds)\label{reduced:BaselineAllAgentsDist2}}
\end{figure}

@@

\begin{algorithm}
\DontPrintSemicolon
\SetAlgoLined
\KwData{$b,S$}
\tcc{$b$ is an agent and $S$ is a set of agents}
\tcc{The set of agent could be provided by an omni directional camera or a set of ultrasonic sensors}
$N \longleftarrow \emptyset$\;
\ForEach(\tcc*{$b^{'}$ is each agent in $S$}){$b^{'}$ in $S$}
{
  \If(\tcc*{$D_b$ is the neighbour range}){$length(bb') < D_{b}$}
  {
     $N \longleftarrow N \cup \{b\}$
  }
}
\tcc{$N$ is a set of Bots $b_1,b_2,\ldots,b_n$}
\KwRet{$N$}
\caption[Neighbour Detection]{nbr(b)}\label{algo:neighbourDetect}
\end{algorithm}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineBasicCountMag1}
\end{center}
\caption{Baseline/basic-count magnitude potential comparison\label{reduced:BaselineBasicCountMag1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineBasicCountDist1}
\end{center}
\caption{Baseline and basic-count distance comparison\label{reduced:BaselineBasicCountDist1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=7cm]{figures/SimpleMulti2}
\end{center}
\caption[Simple multifaceted agents]{Simple multifaceted agents (\textit{screen shot from simulator})\label{reduced:SimpleMulti12}}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[Void and perimeter]{
	 \includegraphics[width=4cm]{figures/PerimeterBots1}
    \label{concave:VoidPerimeter1}
}
\subfigure[Multiple perimeters]{
	 \includegraphics[width=6.5cm]{figures/PerimeterBots2}
    \label{concave:VoidPerimeter2}
}
\caption{Swarm perimeters and voids}
\label{fig:SwarmVoids}
\end{figure}

@@

\begin{algorithm}
\DontPrintSemicolon
\SetAlgoLined
\KwData{$b$}
\tcc{for $nbr()$ see Equation \ref{eq:Neighbours1}}
\If{$|nbr(b)| \leq 4$}{
   \KwRet{True}\;
}
\KwRet{False}\;
\caption{SmallNeighbourCount}\label{SmallNeighbourCount}
\end{algorithm}

@@

\begin{algorithm}
\DontPrintSemicolon
\SetAlgoLined
\caption{NeighbourAngle: Sorted by angle}
\KwData{b}
\tcc{$angles$ is a dictionary of agent/angle}
$angles \leftarrow \emptyset$\;
\For{$b^{'}\in b.neighbours$}{
	\eIf{$b.neighbours[0] == b^{'}$}{
      $angles[b^{'}] = 0$\;
	}{
		$newAngle = b.getAngle(b.neighbours[0], b^{'})$\;
	   $angles[b^{'}] = newAngle$\;
	}
}
\KwRet{$sort(angles)$} 
\label{algo:getNeighbourAngles}
\end{algorithm}

@@

\begin{algorithm}
\DontPrintSemicolon
\SetAlgoLined
\caption{CheckVisibility}
\KwData{b,angles}
\For{$i \leftarrow 0$ \KwTo $size(angles)-1$}{
	\eIf{i == size(angles)-1}{
		\If{$cosrule(b,angles[size(angles)-1][0],angles[i][0]$}{
   		\KwRet{True}
   	}
	}
	{\If{$cosrule(b,angles[i + 1][0],angles[i][0]$}{
			\KwRet{True}
		}
	}
}
\KwRet{False}
\label{algo:checkVisibility}
\end{algorithm}

@@

\begin{algorithm}
\DontPrintSemicolon
\SetAlgoLined
\caption{CheckConvex}
\KwData{angles}
\For{$i \leftarrow 0$ \KwTo $size(angles)-1$}{
	\eIf{i == size(angles)-1}{
		\If{$360 - angles[loop][1] \geq 180$}{
   		\KwRet{True}
   	}
	}{
		\If{$angles[loop + 1][1] - angles[loop][1] \geq 180$}{
			\KwRet{True}
		}
	}
}
\KwRet{False}
\label{algo:checkConvex}
\end{algorithm}

@@

\begin{algorithm}
\DontPrintSemicolon
\SetAlgoLined
\caption{CheckPerimeter}
\KwData{$b,S$}
\If{SmallNeighbourCount(b,S)}{
	\KwRet{True}
}
$angles = NeighbourAngle(b)$\;
\If{CheckVisibility(b,angles)}{
	\If{CheckConvex(angles)}{
		\KwRet{True}
	}
}
\KwRet{False}
\label{algo:checkPerimeter}
\end{algorithm}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineFullPerimeterMag1}
\end{center}
\caption{Baseline/Full perimeter magnitude comparison\label{reduced:BaselineFullPerimeterMag1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineFullPerimeterDist1}
\end{center}
\caption{Baseline/Full perimeter distance comparison\label{reduced:BaselineFullPerimeterDist1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllDist1}
\end{center}
\caption{Baseline distance comparison\label{reduced:BaselineAllDist1}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllDist2}
\end{center}
\caption{Baseline distance comparison\label{reduced:BaselineAllDist2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllMag1}
\end{center}
\caption{Baseline magnitude comparison\label{reduced:BaselineAllMag1}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllMag2}
\end{center}
\caption{Baseline and magnitude comparison\label{reduced:BaselineAllMag2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmPerimeter1}
\end{center}
\caption{200 agent swarm GPS Usage\label{fig:SwarmPerimeter1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmPropagationComparison1}
\end{center}
\caption{Swarm propagation path comparison\label{reduced:SwarmPropagationPathComparison1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmPropagationComparison2}
\end{center}
\caption{Swarm propagation path comparison\label{reduced:SwarmPropagationPathComparison2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmPropagationComparison3}
\end{center}
\caption{Swarm traversal at end of 60s run\label{reduced:SwarmPropagationPathComparison3}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmSpeed1}
\end{center}
\caption{200 agent swarm terminal speed (over 20s period)\label{fig:SwarmSpeed1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmNeighbourCount}
\end{center}
\caption{Neighbour count effect from \textit{destination vectors}\label{fig:SwarmNeighbourCount}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/SwarmNeighbourCountBalanced}
\end{center}
\caption{Neighbour count effect from balanced directional bias\label{fig:SwarmNeighbourCountBalanced}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAll100-60-20-1}
\end{center}
\caption{Swarm distance analysis\label{fig:BaselineAll100-60-20-1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAll100-60-20-2}
\end{center}
\caption{Swarm distance analysis\label{fig:BaselineAll100-60-20-2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllMag100-60-20-1}
\end{center}
\caption{Swarm magnitude analysis\label{fig:BaselineAllMag100-60-20-1}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllMag100-60-20-2}
\end{center}
\caption{Swarm magnitude analysis\label{fig:BaselineAllMag100-60-20-2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=14cm]{figures/BaselineAllPath100-60-20-1}
\end{center}
\caption{Swarm path analysis\label{fig:BaselineAllPath100-60-20-1}}
\end{figure}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Swarm coordination through perimeter detection}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
This paper identifies the effect a \textit{destination vector} has upon the motion of a swarm. Three coordination techniques are applied to a swarm and metrics are used to identify the effects. The three coordination techniques are: full perimeter detection, where only edge based agents will have a \textit{destination vector} applied. Partial perimeter detection, where a subset of the perimeter agents are detected and finally all agents in the swarm having a \textit{destination vector} applied. For all the experiments the base parameters of the swarm are fixed ensuring that the only variable will be the \textit{destination vector} that is applied by the coordinating agents. This process allows the impact of the algorithms to be isolated and compared. Section~\ref{sec:AlternateBias1}~discusses the potential variations to the base parameters and the effects this has on controlling the impact of the weightings.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{figures/SampleSwarm200-1}
\end{center}
\caption[Sample swarm 200 agents initial state]{Sample swarm 200 agents initial state (\textit{screen shot from simulator})\label{fig:SampleSwarm200-1}}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{| p{1.5cm} | c | p{4cm} |}
\hline
\bf Weight \bf Component & \bf Hexagonal & \bf Description \\ \hline
Sample Rate & 100 & ms - Unit sampling interval\\  \hline
$k_c$ & 5 & weight adjuster for cohesion vector\\  \hline
$k_r$ & 15 & weight adjuster for repulsion  vector\\  \hline
$k_d$ & 0/100 & weight adjuster for destination vector 0 for static baseline 100 for destination based\\  \hline
Neighbour Distance & 70 & units\\  \hline
Agent Boundary & 80 & units\\  \hline
Speed & 20 & units/s\\  \hline
\end{tabular}\caption{Swarm Weighted Model} \label{tab:DynamicPhysics1}
\end{center}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineMagnitude1}
\end{center}
\caption{Baseline internal movement - magnitude\label{coord:BaselineMagnitude1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineDistance1}
\end{center}
\caption{Baseline internal movement - distance\label{coord:BaselineDistance1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmPathBaseline}
\end{center}
\caption{Baseline swarm path\label{coord:SwarmPathBaseline1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{figures/Monolithic2}
\end{center}
\caption[Monolithic agents]{Monolithic agents (Circles indicate all agents are using GPS, \textit{screen shot from simulator}) \label{reduced:Monolithic1}}
\end{figure}

\subsection{Baseline and effect of no perimeter detection\label{section:compareBaselineNoPerimeter}}
To identify the effect of the all-agents algorithm the simulation is executed using the same parameters as the baseline swarm with the added \textit{destination vector} on all the agents. The effect of introducing this bias on the swarms internal characteristics is shown in~Figures~\ref{reduced:BaselineAllAgentsMag1} and~\ref{reduced:BaselineAllAgentsDist1}.
%BASELINE-ALLAGENTS-MAG.py
\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllAgentsMag1}
\end{center}
\caption{Baseline/All agents comparison \textit{inter-agent vector} magnitude\label{reduced:BaselineAllAgentsMag1}}
\end{figure}

Figure~\ref{reduced:BaselineAllAgentsMag1} shows the effect on the \textit{inter-agent vector} magnitude of the swarm: the average resultant magnitude is lower than the baseline. This is due to there being a greater distribution of \textit{inter-agent vector} magnitudes from the disturbance caused by the \textit{destination vector} on all of the agents and the swarm is therefore less cohesive. The graph also shows that there is a higher variation from the mean; again this is due to the change in the bias of all the agents. The agents are moving towards a goal and are therefore not moving to an equilibrium distribution. Figure~\ref{reduced:BaselineAllAgentsMag1}~also shows that the \textit{direction vector} increases the time it takes for the swarm to distribute the agents and although the deviation diminishes the swarm cannot overcome the \textit{direction vector's} effect and the swarm appears chaotic.
%BASELINE-ALLAGENTS-DIST.py
\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllAgentsDist1}
\end{center}
\caption{Baseline/All agents comparison (distance)\label{reduced:BaselineAllAgentsDist1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=7cm]{figures/ConicalPath}
\end{center}
\caption{Conical destination trajectories\label{reduced:ConicalPath}}
\end{figure}

This effect can be seen in both the magnitudes shown in~Figure~\ref{reduced:BaselineAllAgentsMag2} and in the distances shown in~Figure~\ref{reduced:BaselineAllAgentsDist2} which both show the averages initially decreasing but then increasing again as the swarm approaches the destination. This is accompanied by a greater standard deviation caused by the \textit{direction vector} affecting the priority of the swarm as agents are drawn to the destination reducing the effect of the \textit{inter-agent vectors} creating stable structures.
%BASELINE-ALLAGENTS-MAG.py
\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllAgentsMag2}
\end{center}
\caption[Baseline/All agents magnitude comparison]{Baseline/All agents \textit{inter-agent vector} magnitude comparison (60 seconds)\label{reduced:BaselineAllAgentsMag2}}
\end{figure}
%BASELINE-ALLAGENTS-DIST.py
\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllAgentsDist2}
\end{center}
\caption{Baseline/All agents distance comparison (60 seconds)\label{reduced:BaselineAllAgentsDist2}}
\end{figure}

@@

\begin{figure}
\begin{algorithmic}[1]
\Procedure{CheckVisibility}{$b,S$}
%\tcc{$b$ is an agent and $S$ is a set of agents}
%\tcc{The set of agent could be provided by an omni directional camera or a set of ultrasonic sensors}
\State $N \longleftarrow \emptyset$\;
\For{$b^{'}$ in $S$}
  \If{$length(bb') < D_{b}$}
     \State $N \longleftarrow N \cup \{b\}$
  \EndIf
\EndFor
%\tcc{$N$ is a set of Bots $b_1,b_2,\ldots,b_n$}
\State\textbf{return} $N$
\EndProcedure
\end{algorithmic}
\caption[Neighbour Detection]{nbr(b)}
\label{algo:neighbourDetect}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineBasicCountMag1}
\end{center}
\caption{Baseline/basic-count magnitude potential comparison\label{reduced:BaselineBasicCountMag1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineBasicCountDist1}
\end{center}
\caption{Baseline and basic-count distance comparison\label{reduced:BaselineBasicCountDist1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{figures/SimpleMulti2}
\end{center}
\caption[Simple multifaceted agents]{Simple multifaceted agents (\textit{screen shot from simulator})\label{reduced:SimpleMulti12}}
\end{figure}

@@

\begin{figure}
\begin{center}
	 \includegraphics[width=4cm]{figures/PerimeterBots1}\label{concave:VoidPerimeter1}
\end{center}
\caption{Void and perimeter}
\label{concave:VoidPerimeter1}
\end{figure}

\begin{figure}
\begin{center}
	 \includegraphics[width=4cm]{figures/PerimeterBots2}\label{concave:VoidPerimeter2}
\end{center}
\caption{Multiple perimeters}
\label{concave:VoidPerimeter2}
\end{figure}

%% \begin{figure}
%% \centering
%% \subfigure[Void and perimeter]{
%% 	 \includegraphics[width=4cm]{figures/PerimeterBots1}
%%     \label{concave:VoidPerimeter1}
%% }
%% \subfigure[Multiple perimeters]{
%% 	 \includegraphics[width=6.5cm]{figures/PerimeterBots2}
%%     \label{concave:VoidPerimeter2}
%% }
%% \caption{Swarm perimeters and voids}
%% \label{fig:SwarmVoids}
%% \end{figure}

@@

\begin{figure}
\begin{algorithmic}[1]
\Procedure{NeighbourCount}{$b$}
\If{$|nbr(b)| \leq 4$}
   \State\textbf{return} $True$
\EndIf
\State\textbf{return} $False$
\EndProcedure
\end{algorithmic}
\caption{SmallNeighbourCount}
\label{SmallNeighbourCount}
\end{figure}

@@

\begin{figure}
\begin{algorithmic}[1]
\Procedure{NeighbourAngle}{$b$}
\State $angles \leftarrow \emptyset$
\For{$b^{'}\in b.neighbours$}
	\If{$b.neighbours[0] == b^{'}$}
      \State $angles[b^{'}] = 0$
	\Else
		\State $newAngle = b.getAngle(b.neighbours[0], b^{'})$
	   \State $angles[b^{'}] = newAngle$
	\EndIf
\EndFor
\State \textbf{return}{$sort(angles)$} 
\EndProcedure
\end{algorithmic}
\caption{NeighbourAngle: Sorted by angle}
\label{algo:getNeighbourAngles}
\end{figure}

@@

\begin{figure}
\begin{algorithmic}[1]
\Procedure{NeighbourAngle}{$b,angles$}
\For{$i \leftarrow 0$ to $size(angles)-1$}
	\If{i == size(angles)-1}
		\If{$cosrule(b,angles[size(angles)-1][0],angles[i][0]$}
			\State \textbf{return} $True$ 
   	\EndIf
	\ElsIf{$cosrule(b,angles[i + 1][0],angles[i][0]$}
		\State \textbf{return} $True$ 
	\EndIf
\EndFor
\State \textbf{return} $False$ 
\EndProcedure
\end{algorithmic}
\caption{CheckVisibility}
\label{algo:checkVisibility}
\end{figure}

%% \begin{algorithm}
%% \DontPrintSemicolon
%% \SetAlgoLined
%% \caption{CheckVisibility}
%% \KwData{b,angles}
%% \For{$i \leftarrow 0$ \KwTo $size(angles)-1$}{
%% 	\eIf{i == size(angles)-1}{
%% 		\If{$cosrule(b,angles[size(angles)-1][0],angles[i][0]$}{
%%    		\KwRet{True}
%%    	}
%% 	}
%% 	{\If{$cosrule(b,angles[i + 1][0],angles[i][0]$}{
%% 			\KwRet{True}
%% 		}
%% 	}
%% }
%% \KwRet{False}
%% \label{algo:checkVisibility}
%% \end{algorithm}

@@

\begin{figure}
\begin{algorithmic}[1]
\Procedure{CheckConvex}{$angles$}
\For{$i \leftarrow 0$ to $size(angles)-1$}
	\If{i == size(angles)-1}
		\If{$360 - angles[loop][1] \geq 180$}
			\State \textbf{return} $True$ 
   	\EndIf
	\ElsIf{$angles[loop + 1][1] - angles[loop][1] \geq 180$}
		\State \textbf{return} $True$ 
	\EndIf
\EndFor
\State \textbf{return} $False$ 
\EndProcedure
\end{algorithmic}
\caption{CheckConvex}
\label{algo:checkConvex}
\end{figure}

%% \begin{algorithm}
%% \DontPrintSemicolon
%% \SetAlgoLined
%% \caption{CheckConvex}
%% \KwData{angles}
%% \For{$i \leftarrow 0$ \KwTo $size(angles)-1$}{
%% 	\eIf{i == size(angles)-1}{
%% 		\If{$360 - angles[loop][1] \geq 180$}{
%%    		\KwRet{True}
%%    	}
%% 	}{
%% 		\If{$angles[loop + 1][1] - angles[loop][1] \geq 180$}{
%% 			\KwRet{True}
%% 		}
%% 	}
%% }
%% \KwRet{False}
%% \label{algo:checkConvex}
%% \end{algorithm}

@@

\begin{figure}
\begin{algorithmic}[1]
\Procedure{CheckPerimeter}{$b,S$}
\If{SmallNeighbourCount(b,S)}
	\State \textbf{return} $False$ 
\EndIf
\State $angles = NeighbourAngle(b)$
\If{CheckVisibility(b,angles)}
	\If{CheckConvex(angles)}
		\State \textbf{return} $True$ 
	\EndIf
\EndIf
\State \textbf{return} $False$ 
\EndProcedure
\end{algorithmic}
\caption{CheckPerimeter}
\label{algo:checkPerimeter}
\end{figure}

%% \begin{algorithm}
%% \DontPrintSemicolon
%% \SetAlgoLined
%% \caption{CheckPerimeter}
%% \KwData{$b,S$}
%% \If{SmallNeighbourCount(b,S)}{
%% 	\KwRet{True}
%% }
%% $angles = NeighbourAngle(b)$\;
%% \If{CheckVisibility(b,angles)}{
%% 	\If{CheckConvex(angles)}{
%% 		\KwRet{True}
%% 	}
%% }
%% \KwRet{False}
%% \label{algo:checkPerimeter}
%% \end{algorithm}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineFullPerimeterMag1}
\end{center}
\caption{Baseline/Full perimeter magnitude comparison\label{reduced:BaselineFullPerimeterMag1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineFullPerimeterDist1}
\end{center}
\caption{Baseline/Full perimeter distance comparison\label{reduced:BaselineFullPerimeterDist1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllDist1}
\end{center}
\caption{Baseline distance comparison\label{reduced:BaselineAllDist1}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllDist2}
\end{center}
\caption{Baseline distance comparison\label{reduced:BaselineAllDist2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllMag1}
\end{center}
\caption{Baseline magnitude comparison\label{reduced:BaselineAllMag1}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllMag2}
\end{center}
\caption{Baseline and magnitude comparison\label{reduced:BaselineAllMag2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmPerimeter1}
\end{center}
\caption{200 agent swarm GPS Usage\label{fig:SwarmPerimeter1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmPropagationComparison1}
\end{center}
\caption{Swarm propagation path comparison\label{reduced:SwarmPropagationPathComparison1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmPropagationComparison2}
\end{center}
\caption{Swarm propagation path comparison\label{reduced:SwarmPropagationPathComparison2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmPropagationComparison3}
\end{center}
\caption{Swarm traversal at end of 60s run\label{reduced:SwarmPropagationPathComparison3}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmSpeed1}
\end{center}
\caption{200 agent swarm terminal speed (over 20s period)\label{fig:SwarmSpeed1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmNeighbourCount}
\end{center}
\caption{Neighbour count effect from \textit{destination vectors}\label{fig:SwarmNeighbourCount}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/SwarmNeighbourCountBalanced}
\end{center}
\caption{Neighbour count effect from balanced directional bias\label{fig:SwarmNeighbourCountBalanced}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAll100-60-20-1}
\end{center}
\caption{Swarm distance analysis\label{fig:BaselineAll100-60-20-1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAll100-60-20-2}
\end{center}
\caption{Swarm distance analysis\label{fig:BaselineAll100-60-20-2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllMag100-60-20-1}
\end{center}
\caption{Swarm magnitude analysis\label{fig:BaselineAllMag100-60-20-1}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllMag100-60-20-2}
\end{center}
\caption{Swarm magnitude analysis\label{fig:BaselineAllMag100-60-20-2}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineAllPath100-60-20-1}
\end{center}
\caption{Swarm path analysis\label{fig:BaselineAllPath100-60-20-1}}
\end{figure}
